Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-20 SDSS-2023/testing-charts-accuracy.qmd
table of rounds with lambda

knitr::opts_chunk$set(
  jds.rmd::pdf_article()$knitr
)

@@

@@

\kr{Should the abstract match -- or be close to -- our SDSS short abstract?}

@@

Cleveland and McGill's work -- while a foundational user study in graphical perception -- utilized a small convenience sample, consisting of only a few individuals recruited from among the authors' coworkers and their spouses.
@heerCrowdsourcingGraphicalPerception2010 reproduced Cleveland and McGill's rankings using a larger sample from a crowd sourcing platform.
A total of XXX Amazon Mechanical Turkers were involved.
Crowd sourced samples were shown by @borgoCrowdsourcingInformationVisualization2017 to be biased towards more male, younger, and relatively higher education relative to the adult U.S. population as a whole.
These study populations are thus not representative of the general population, a common target audience for data visualization and scientific communication work.
Further, the populations' emphasis on higher education individuals also leads to results which hold for groups of individuals who may be more likely to have prior exposure to data visualization in the context of scientific communication, or more exposure to data topics in higher education, but may not hold across other groups within the population.
\kr{I don't know if the prior statement is going too far? Maybe we can rephrase.}

<!-- Bias from crowd-sourcing? sample size?  -->

@@

```{r}
#| label: fig-tasks-explain
#| fig-cap: Comparisons made in charts across tasks 1 through 3 within the Cleveland and McGill ranking

@@

```{r}
#| label: fig-tasks
#| fig-cap: "Each of the visual stimuli presented to viewers. In each bar chart, two pieces are marked. The larger piece in each chart are pieces B and D. "
#| fig-subcap:
#| - "Vertical stacked bar, unaligned"
#| - "Horizontal stacked bar, unaligned"
#| - "Wide horizontal stacked bar, unaligned"
#| - "Vertical stacked bar, aligned"
#| - "Horizontal stacked bar, aligned"
#| - "Wide horizontal stacked bar, aligned"
#| layout-nrow: 2
#| out-width: 100%
knitr::include_graphics("images/vertical-ab.PNG")
knitr::include_graphics("images/round3/horizontal-ab.PNG")
knitr::include_graphics("images/round3/hwide-ab.PNG")
knitr::include_graphics("images/vertical-cd.PNG")
knitr::include_graphics("images/round3/horizontal-cd.PNG")
knitr::include_graphics("images/round3/hwide-cd.PNG")
```

@@

\kr{We need to be careful about not making it seem like the rounds are the same as the tasks, since we have 3 rounds and 3 tasks. We describe it, but I feel like this table kind of muddies the waters. Could we instead do a table of respondents by task?}

| Name    | Date       |      \# Participants |                effective sample size |         Sum of weights $\sum_i w_i$ |
|---------------|---------------|--------------:|--------------:|--------------:|
| Round 1 | April 2022 | `r nrow(round1_adj)` | `r round(neff(round1_adj$weight),1)` | `r round(sum(round1_adj$weight),1)` |
| Round 2 | May 2022   | `r nrow(round2_adj)` | `r round(neff(round2_adj$weight),1)` | `r round(sum(round2_adj$weight),1)` |
| Round 3 | Jun 2022   | `r nrow(round3_adj)` | `r round(neff(round3_adj$weight),1)` | `r round(sum(round3_adj$weight),1)` |
|         |            |                      |                                      |                                     |

: Survey rounds: dates, number of participants (nominal sample size), effective sample size, and sum of weights. {#tbl-rounds}

@@

>>>>

@@

lambdas <- c(lambda_1_2, 1-lambda_1_2)*lambda_12_3
lambdas <- c(lambdas, 1-sum(lambdas))

@@

\kr{Should the abstract match -- or be close to -- our SDSS short abstract?}
\hh{I don't think it has to}

@@

Cleveland and McGill's work -- while a foundational user study in graphical perception -- utilized a small convenience sample, consisting of only a few individuals recruited from among the authors' coworkers and their spouses.
@heerCrowdsourcingGraphicalPerception2010 reproduced Cleveland and McGill's rankings using a larger sample from a crowd sourcing platform.
A total of XXX Amazon Mechanical Turkers were involved.
Crowd sourced samples were shown by @borgoCrowdsourcingInformationVisualization2017 to be biased towards more male, younger, and relatively higher education relative to the adult U.S. population as a whole.
These study populations are thus not representative of the general population, a common target audience for data visualization and scientific communication work.
Further, the populations' emphasis on higher education individuals also leads to results which hold for groups of individuals who may be more likely to have prior exposure to data visualization in the context of scientific communication, or more exposure to data topics in higher education, but may not hold across other groups within the population.
\kr{I don't know if the prior statement is going too far? Maybe we can rephrase.}
\hh{I think this is going to hold - the demographics are pretty significant}
<!-- Bias from crowd-sourcing? sample size?  -->

@@

```{=tex}
\hh{I think we should include the floating bars here to demonstrate that they are worse than the wide horizontal bars. }
```

```{r}
#| label: fig-tasks-explain
#| fig-cap: Comparisons made in charts within the Cleveland and McGill ranking 
#| out-width: 60%

@@

```{r}
#| label: fig-tasks
#| fig-cap: "Each of the visual stimuli presented to viewers. In each bar chart, two pieces are marked. The larger piece in each chart are pieces B and D. "
#| fig-subcap:
#| - "Vertical stacked bar, unaligned"
#| - "Horizontal stacked bar, unaligned"
#| - "Wide horizontal stacked bar, unaligned"
#| - "Vertical stacked bar, aligned"
#| - "Horizontal stacked bar, aligned"
#| - "Wide horizontal stacked bar, aligned"
#| layout-nrow: 2
#| out-width: 90%
knitr::include_graphics("images/vertical-ab.PNG")
knitr::include_graphics("images/round3/horizontal-ab.PNG")
knitr::include_graphics("images/round3/hwide-ab.PNG")
knitr::include_graphics("images/vertical-cd.PNG")
knitr::include_graphics("images/round3/horizontal-cd.PNG")
knitr::include_graphics("images/round3/hwide-cd.PNG")
```

@@

\kr{We need to be careful about not making it seem like the rounds are the same as the tasks, since we have 3 rounds and 3 tasks. We describe it, but I feel like this table kind of muddies the waters. Could we instead do a table of respondents by task?} \hh{does this comment still stand after the re-organization? ... I would suggest to move it up to the survey methods and add the lambdas}

| Name    | Date       |      \# Participants |                effective sample size |         Sum of weights $\sum_i w_i$ | $\lambda_i$ |
|---------------|---------------|--------------:|--------------:|--------------:|--------------:|
| Round 1 | April 2022 | `r nrow(round1_adj)` | `r round(neff(round1_adj$weight),1)` | `r round(sum(round1_adj$weight),1)` | $\lambda_1$  =  `r round(lambdas[1],3)` |
| Round 2 | May 2022   | `r nrow(round2_adj)` | `r round(neff(round2_adj$weight),1)` | `r round(sum(round2_adj$weight),1)` | $\lambda_2$  = `r sprintf("%.3f",lambdas[2])` |
| Round 3 | Jun 2022   | `r nrow(round3_adj)` | `r round(neff(round3_adj$weight),1)` | `r round(sum(round3_adj$weight),1)` | $\lambda_3$  = `r round(lambdas[3],3)` |
| **Total**        |    ---        |    `r nrow(round_123)`   |  `r round(neff(round_123$weight),1)`   |    |  $\lambda_1w_1 + \lambda_2w_2 + \lambda_3w_3$ |

: Survey rounds: dates, number of participants (nominal sample size), effective sample size, sum of weights, and factors for the convex combination as discussed above. {#tbl-rounds}

@@

```{r}

sum(round_123$weight)
